---
title: "Space Elasticity Transformation"
output: html_notebook
---

This script will provide utility functions to transform space elasticity curve
These transformations will enable to adjust the curve for store specific parameters

There are four types of transformations:
* Additive - Add given list of values to each point in the space elasticity curve
* Multiplicative - Multiply given list of values to each point in the space elasticity curve
* Exponential - Multiply exponential value of given list to each point in the space elasticity curve
* Logarithmic - Multiply logarithmic value of given list to each point in the space elasticity curve

#####

Loading base dataset to see how will transformation look like
```{r setup}
knitr::opts_chunk$set(root.dir="/home/pushkar/scalene")
library("reshape2")
```

```{r}
getwd()
# knitr::opts_chunk$set(root.dir="/home/pushkar/scalene")
# knitr::opts_knit$set(root.dir="/home/pushkar/scalene")
setwd("/home/pushkar/scalene")
getwd()
print(knitr::opts_chunk$get("root.dir"))
source("R/utils/scalene_utilities.R")
source("conf/spaceopt_config.R")
source("R/spaceopt/scoring/space_elasticity_transformation.R")
library("ggplot2")
SPACE_ELASTICITY_PARAMS_DB <- read.csv("data/spaceopt/output/Space_Elasticity_Params_DB.csv",
                                       stringsAsFactors = F)
```

Lets take a specific product and illustrate the transformation functions
```{r}
i = 50
space_params <- c(SPACE_ELASTICITY_PARAMS_DB$ALPHA[i],
                  SPACE_ELASTICITY_PARAMS_DB$BETA[i],
                  SPACE_ELASTICITY_PARAMS_DB$GAMMA[i],
                  SPACE_ELASTICITY_PARAMS_DB$DELTA[i])
rm(SPACE_ELASTICITY_PARAMS_DB)
curve_data <- data.frame(SPACE=seq(1,25))
curve_data$BASE_KPI <- space_elasticity_values(space_params,curve_data$SPACE)
# curve_data now has the space and corresponding cumulative KPI
head(curve_data)
```

The base elasticity curve looks as follows:
```{r}
p <- ggplot(data = curve_data) + geom_line(aes(x=SPACE,y=BASE_KPI)) + ggtitle("Base Space Elasticity Curve") + expand_limits(x = 0,y=0) + scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) + ylab("Cumulative KPI")
p
```

And now we will see how the base curve can be transformed.

# Additive Transformation
We want to add a value to each of the points of base elasticity curve
If the elasticity curve is to be shifted upwards, then we will add a positive value.
A negative value will bring down the elasticity curve.

Note that if we add a constant value to all the points of elasticity curve, then the marginal elasticity curve will not change (except for the first unit of space)

We will now see how the curve shifts when we add values to the base curve.
```{r}
mod_values <- seq(from = 10000, to = 1000, length.out = length(curve_data$BASE_KPI))
p <- ggplot() + geom_line(aes(x=curve_data$SPACE,y=mod_values)) + ggtitle("Modifying values") + expand_limits(x=0,y=0) + ylab("Mod values") + xlab("SPACE")
p

```

And the transformed space elasticity curve looks like:
```{r}
curve_data$ADD_KPI <- elasticity_transformation(curve_values = curve_data$BASE_KPI,
                                                modifying_values = mod_values,
                                                transformType = "ADD")
curve_data.m <- melt(data = curve_data,
                     id.vars = c("SPACE"),
                     value.name = "VALUE",
                     variable.name = "TYPE")

p <- ggplot(curve_data.m, aes(x=SPACE,y=VALUE,colour=TYPE)) + geom_line() + scale_color_brewer(palette = COLOR_PALETTE) + ggtitle("Additive Transformation") + theme_dark()
p
```
**UPDATE: transformation function now returns an increasing function**

~~We see the error in above graph. We need to ensure that the KPI is an increasing function with Space.~~

# Multiplicative transformation
```{r}
mod_values <- seq(from=2, to=1, length.out = length(curve_data$SPACE))
p <- ggplot() + geom_line(aes(x=curve_data$SPACE,y=mod_values)) + ggtitle("Modifying values") + xlab("SPACE") + ylab("Modifying values") + expand_limits(x=0,y=0) + scale_color_brewer(palette = COLOR_PALETTE) + theme_grey()
p
```
And the transformed space elasticity curves look like this:

```{r}
curve_data$MUL_KPI <- elasticity_transformation(curve_values = curve_data$BASE_KPI,
                                                modifying_values = seq(from=2,to=1,length.out = length(curve_data$SPACE)),
                                                transformType = "MUL")
curve_data.m <- melt(data = curve_data,
                     id.vars = c("SPACE"),
                     value.name = "VALUE",
                     variable.name = "TYPE")

p <- ggplot(curve_data.m, aes(x=SPACE,y=VALUE,colour=TYPE)) + geom_line() + scale_color_brewer(palette = COLOR_PALETTE) + ggtitle("Multiplicative Transformation") + theme_grey()
p
```

